Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India

### 2023-04-21 outputs/paper/paper.qmd
Update version with citations

library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)
library(ggalt)
library(broom)
library(kableExtra)

@@

The issue of colorism has been a persistent and pervasive concern across the world. In societies where attractiveness is highly valued, women often rely on makeup to enhance their appearance, with companies capitalizing on these insecurities to promote their products. With the growing popularity of makeup brands, the beauty industry has perpetuated and exacerbated colorism, particularly in Japan and India, which are among the largest beauty markets in Asia (CITATION).

The roots of colorism in Japan and India have historical and cultural origins that have contributed to the perpetuation of this issue in modern society. In Japan, the association of fair skin with beauty and status can be traced back to its aristocracy, who were able to avoid outdoor labour and maintain a pale complexion (CITATION). This idea became ingrained in Japanese society and is reinforced through media, advertising, and popular culture. The influence of Western beauty standards, introduced through the influx of mass media from the United States after World War II, has also contributed to the shift towards lighter skin tones in Japan (CITATION).

Similarly, in India, the issue of colorism has been exacerbated by the history of colonialism, with the British favouring Indians with lighter skin for government jobs. This discrimination based on skin colour has persisted in Indian society, with fair skin being equated with higher social status and dark skin being associated with lower status (CITATION). The impacts of colorism in India are widespread, affecting social mobility, education, employment, and marriage.

In addition to the negative impact on individuals, colorism also has wider societal consequences. Individuals with darker skin tones face exclusion and marginalization, as well as limited access to products and services, leading to unequal opportunities in various aspects of life (CITATION). The globalization of beauty standards has further compounded the issue, with Western ideals of beauty being prioritized and perpetuated by the beauty industry.

To better understand the issue of colorism in Japan and India, the present study draws on data from an article published by The Pudding, a digital publisher specializing in data journalism. The original article examined the lack of diversity in makeup shades offered by major cosmetic brands (CITATION). However, the current study will focus specifically on the context of Asia and the role of colorism in perpetuating limited shade ranges, with a particular focus on Japan and India.

@@

The primary tool used to analyse data in this paper is R, an open-source statistical programming language [@cite_tool_r]. The paper also uses a number of R packages, including: dplyr [@cite_tool_dplyr], foreign [@cite_tool_foreign], ggplot2 [@cite_tool_ggplot2], here [@cite_tool_here], janitor [@cite_tool_janitor], kableExtra [@cite_tool_kableextra], knitr [@cite_tool_knitr], lubridate [@cite_tool_lubridate], readr [@cite_tool_readr], RColorBrewer [@cite_tool_rcolorbrewer], scales [@cite_tool_scales], and tidyverse [@cite_tool_tidyverse].

@@

The dataset was specifically curated for application in The Pudding essay entitled "Beauty Brawl," which was published in June of 2018 (CITATION). The data was obtained through a systematic process that involved identifying prominent beauty brands in the United States, Nigeria, India, and Japan, as well as consulting various sources that verified their status as best-selling products within their respective domestic markets. The research team accessed each of the brand's official websites in May of 2018 and isolated their liquid foundation collection that possessed the most extensive variety of available shades. For each colour swatch displayed for the product, the corresponding hex colour values were recorded. Subsequently, Adobe Photoshop was utilized to extract the lightness value of each colour using the CIE Lab colour model.

@@

Moreover, it is worth noting that each product within the dataset is exclusively assigned to a single group. In the dataset, a total of seven distinct groups were employed for classification:
 • 0: Fenty Beauty's PRO FILT'R Foundation Only
 • 1: Make Up For Ever's Ultra HD Foundation Only
 • 2: US Best Sellers
 • 3: BIPOC-recommended Brands with BIPOC Founders
 • 4: BIPOC-recommended Brands with White Founders
 • 5: Nigerian Best Sellers
 • 6: Japanese Best Sellers
 • 7: Indian Best Sellers

The dataset included information on the hexadecimal colour code (hex), hue (angle on the colour wheel), saturation (degree of colour/chroma), and brightness (also known as value, which measures the lightness or darkness halfway point) values of the foundation shades. The lightness (the relative degree of black or white) values were derived using the CIE Lab colour model, which is predicated on the human perception of colour. The numerical values in the CIE Lab model describe the full spectrum of colours that are visible to individuals with normal vision. As the CIE Lab model represents how a colour appears rather than specifying the quantity of a particular colourant required for a particular device (such as a digital camera, monitor, or desktop printer) to generate colours, it is regarded as a device-independent colour model. To ensure reliable and consistent colour transformation from one colour space to another, colour management systems use the CIE Lab model as a reference point (CITATION).

@@

#TABLE 2 - Total number of products by lightness range 
 summary <- brand_origin |>
  tabyl(group, light_range) |>
  adorn_totals("col")

@@

summary |>
  kable() |>
  kable_styling(full_width = F) |>
  add_header_above(c(" " = 1, "Lightness Range" = 6))

@@

# figure 1 - Distribution by Lightness
#Japan & India by domestic/international

brand_origin |>
  ggplot(aes(x = group, y = L, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Lightness",
    color = "Country",
    title = "Distribution of Foundation Lightness between Domestic and International Brands",
    caption = "Data source: The Pudding.")

#figure 2 - Distribution by Saturation
brand_origin |>
  ggplot(aes(x = group, y = S, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 1, 0.05)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Saturation",
    color = "Country",
    title = "Distribution of Foundation Saturation between Domestic and International Brands",
    caption = "Data source: The Pudding")

@@

L = β0 + β1*S + ε

Where:
•	L represents the dependent variable, which is the overall lightness of the foundation shade
•	S represents the independent variable, which is the saturation of the foundation shade
•	β0 represents the intercept of the regression line, which is the predicted value of L when S is equal to zero
•	β1 represents the slope of the regression line, which is the change in L for a one-unit increase in S
•	ε represents the random error term, which accounts for variability in L that is not explained by the relationship with S

The aim of linear regression is to estimate the values of β0 and β1 that minimize the sum of squared errors between the predicted and actual values of lightness (L) for the given values of saturation (S) in the dataset. By minimizing this sum of squared errors, the linear regression model can produce the best-fit line to describe the linear relationship between the two variables, allowing for the estimation of L values based on known S values.

In this project, the lightness variable (L) is measured on a scale of 0 to 100, while the saturation variable (S) is measured on a scale of 0 to 1. Therefore, the slope coefficient β1 in the linear regression model would represent the change in lightness (L) for a one-unit increase in saturation (S), where a one-unit increase in S corresponds to an increase of 1/100 in the saturation of the foundation shade. The intercept β0 in the model would represent the expected value of L when S is equal to zero, which in this case would correspond to the lightness value for a completely desaturated foundation shade.

@@

#Table 3 - Regression Results

@@

kbl(summary, caption = "Linear Regression Model Summary") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#Figure 3 - Linear regression plot

brand_origin |>
  ggplot(mapping = aes(x = S, y = L)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  scale_y_continuous(breaks=seq(0, 100, 10)) +
  scale_x_continuous(breaks=seq(0, 10, 0.10)) +
  theme_minimal() +
  labs(
    y = "Lightness", 
    x = "Saturation"
  )

@@

# figure 4 - Japanese brands and their products

brand_origin |>
  filter(group == 'Japan') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.2) +
  facet_wrap(vars(brand)) +
  scale_x_continuous(breaks=seq(50, 100, 5)) +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation",
    title = "Japanese Brands and their relationship between Lightness and Saturation", 
    caption = "Data source: The Pudding")

@@

In Japan, a negative linear relationship between the saturation and lightness of foundation shades is observed, as depicted in Figure 4. The data indicates that as the lightness of foundation shades increases, their saturation decreases, suggesting that lighter foundations tend to appear ashier or cooler-toned than their darker counterparts. According to a study conducted by L’Oréal, East Asian women have a skin tone range of 55-75 in lightness with warmer tones. The brands closest to the regression line seen in Figure 3 with the widest range in lightness and saturation are Addiction, NARS, and Shu Uemera, as demonstrated in Figure 4.

@@

The data suggest that foundation offerings in Japan tend to skew toward the fairer end of the skin tone range or significantly lighter. While there are options available for Japanese consumers to find foundation within their skin-tone range, the average foundation shade is lighter and ashier, reflecting a preference for fairer skin, and reinforcing the notion that lighter skin is more desirable. This reinforces the societal pressure to conform to certain beauty standards and can exacerbate colourism by perpetuating the notion that lighter skin is superior to darker skin tones. The negative correlation between saturation and lightness observed in the data also implies that consumers with warmer undertones may encounter difficulties in finding foundation shades that strike the appropriate balance between warmth and lightness. Specifically, they may find that foundation shades with warm undertones are excessively dark, while those with cooler undertones are excessively light. This highlights the necessity for makeup brands to provide a diverse range of foundation shades that cater to a variety of undertones and levels of saturation.

@@

#Figure 5 - Indian Brands and their Products
brand_origin |>
  filter(group == 'India') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.5) +
  facet_wrap(vars(brand), scales = "free") +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation",
    title = "Indian Brands and their relationship between Lightness and Saturation", 
    caption = "Data source: The Pudding")

@@

Figure 5 presents a noteworthy disparity in the distribution of foundation shades across various brands concerning their lightness and saturation attributes. Specifically, it appears that domestic brands in India offer fewer foundation shades compared to international brands like L’Oréal and Maybelline. However, despite Indian skin tones falling within a lightness range of 30-65 and exhibiting warm-toned features, the majority of foundation shades offered by international brands are noticeably situated in the 70-85 lightness range. This observation suggests that international brands tend to prioritize whiteness more than local brands.

@@

@@

## Appendix

## References

>>>>

library(tidyverse)
library(dplyr)
library(tidyr)
library(knitr)
library(janitor)
library(scales)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)
library(kableExtra)
library(broom)

@@

The issue of colorism has been a persistent and pervasive concern across the world. In societies where attractiveness is highly valued, women often rely on makeup to enhance their appearance, with companies capitalizing on these insecurities to promote their products. With the growing popularity of makeup brands, the beauty industry has perpetuated and exacerbated colorism, particularly in Japan and India, which are among the largest beauty markets in Asia.

The roots of colorism in Japan and India have historical and cultural origins that have contributed to the perpetuation of this issue in modern society. In Japan, the association of fair skin with beauty and status can be traced back to its aristocracy, who were able to avoid outdoor labour and maintain a pale complexion [@japan]. This idea became ingrained in Japanese society and is reinforced through media, advertising, and popular culture. The influence of Western beauty standards, introduced through the influx of mass media from the United States after World War II, has also contributed to the shift towards lighter skin tones in Japan [@japan].

Similarly, in India, the issue of colorism has been exacerbated by the history of colonialism, with the British favouring Indians with lighter skin for government jobs. This discrimination based on skin colour has persisted in Indian society, with fair skin being equated with higher social status and dark skin being associated with lower status [@india]. The impacts of colorism in India are widespread, affecting social mobility, education, employment, and marriage.

In addition to the negative impact on individuals, colorism also has wider societal consequences. Individuals with darker skin tones face exclusion and marginalization, as well as limited access to products and services, leading to unequal opportunities in various aspects of life [@japan]. The globalization of beauty standards has further compounded the issue, with Western ideals of beauty being prioritized and perpetuated by the beauty industry.

To better understand the issue of colorism in Japan and India, the present study draws on data from an article published by The Pudding, a digital publisher specializing in data journalism. The original article examined the lack of diversity in makeup shades offered by major cosmetic brands [@pudding]. However, the current study will focus specifically on the context of Asia and the role of colorism in perpetuating limited shade ranges, with a particular focus on Japan and India.

@@

This paper was produced using the R statistical programming language [@citeR]. here was used to reference file locations [@here]. The data was examined and cleaned using the packages janitor [@janitor], dplyr [@dplyr], and tidyverse [@tidyverse]. Tables were made knitr [@knitr] and broom [@broom], and formatted with kableExtra [@kableExtra]. ggplot2 [@ggplot2] was used to plot and scale the graphs.

@@

The dataset was specifically curated for application in The Pudding essay entitled "Beauty Brawl," which was published in June of 2018 [@pudding]. The data was obtained through a systematic process that involved identifying prominent beauty brands in the United States, Nigeria, India, and Japan, as well as consulting various sources that verified their status as best-selling products within their respective domestic markets. The research team accessed each of the brand's official websites in May of 2018 and isolated their liquid foundation collection that possessed the most extensive variety of available shades. For each colour swatch displayed for the product, the corresponding hex colour values were recorded. Subsequently, Adobe Photoshop was utilized to extract the lightness value of each colour using the CIE Lab colour model.

@@

Moreover, it is worth noting that each product within the dataset is exclusively assigned to a single group. In the dataset, a total of seven distinct groups were employed for classification:

 * 0: Fenty Beauty's PRO FILT'R Foundation Only
 * 1: Make Up For Ever's Ultra HD Foundation Only
 * 2: US Best Sellers
 * 3: BIPOC-recommended Brands with BIPOC Founders
 * 4: BIPOC-recommended Brands with White Founders
 * 5: Nigerian Best Sellers
 * 6: Japanese Best Sellers
 * 7: Indian Best Sellers

The dataset included information on the hexadecimal colour code (hex), hue (angle on the colour wheel), saturation (degree of colour/chroma), and brightness (also known as value, which measures the lightness or darkness halfway point) values of the foundation shades. The lightness (the relative degree of black or white) values were derived using the CIE Lab colour model, which is predicated on the human perception of colour. The numerical values in the CIE Lab model describe the full spectrum of colours that are visible to individuals with normal vision. As the CIE Lab model represents how a colour appears rather than specifying the quantity of a particular colourant required for a particular device (such as a digital camera, monitor, or desktop printer) to generate colours, it is regarded as a device-independent colour model. To ensure reliable and consistent colour transformation from one colour space to another, colour management systems use the CIE Lab model as a reference point [@adobe].

@@

#Create table to summarize lightness range

 summary <- brand_origin |>
  tabyl(group, light_range) |>
  adorn_totals("col")

@@

summary |>
  kable(caption = "Table 1: Total number of products by lightness range in India & Japan") |>
  kable_styling(full_width = F) |>
  add_header_above(c(" " = 1, "Lightness Range" = 6))

@@

#plot graph to show shade distribution by lightness

brand_origin |>
  ggplot(aes(x = group, y = L, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Lightness",
    title = "Fig. 1: Shade Distribution by Lightness: Domestic vs. International Brands",
    color = "Country",
    caption = "Data source: The Pudding.")
```

#plot graph to show shade distribution by saturation

brand_origin |>
  ggplot(aes(x = group, y = S, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 1, 0.05)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Saturation",
    color = "Country",
    title = "Fig. 2: Shade Distribution by Saturation: Domestic vs. International Brands",
    caption = "Data source: The Pudding")

@@

$$L = \beta_0 + \beta_1S + \epsilon$$

Where:

- $L$ represents the dependent variable, which is the overall lightness of the foundation shade
- $S$ represents the independent variable, which is the saturation of the foundation shade
- $\beta_0$ represents the intercept of the regression line, which is the predicted value of $L$ when $S$ is equal to zero
- $\beta_1$ represents the slope of the regression line, which is the change in $L$ for a one-unit increase in $S$
- $\epsilon$ represents the random error term, which accounts for variability in $L$ that is not explained by the relationship with $S$

The aim of linear regression is to estimate the values of $\beta_0$ and $\beta_1$ that minimize the sum of squared errors between the predicted and actual values of lightness ($L$) for the given values of saturation ($S$) in the dataset. By minimizing this sum of squared errors, the linear regression model can produce the best-fit line to describe the linear relationship between the two variables, allowing for the estimation of $L$ values based on known $S$ values.

In this project, the lightness variable ($L$) is measured on a scale of 0 to 100, while the saturation variable ($S$) is measured on a scale of 0 to 1. Therefore, the slope coefficient $\beta_1$ in the linear regression model would represent the change in lightness ($L$) for a one-unit increase in saturation ($S$), where a one-unit increase in $S$ corresponds to an increase of 1/100 in the saturation of the foundation shade. The intercept $\beta_0$ in the model would represent the expected value of $L$ when $S$ is equal to zero, which in this case would correspond to the lightness value for a completely desaturated foundation shade.

@@

# create table to summarize regression findings

@@

kbl(summary, caption = "Table 2: Linear Regression Model Summary") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

#plot graph to show linear regression

brand_origin |>
  ggplot(mapping = aes(x = S, y = L)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  scale_y_continuous(breaks=seq(0, 100, 10)) +
  scale_x_continuous(breaks=seq(0, 10, 0.10)) +
  theme_minimal() +
  labs(
    y = "Lightness", 
    x = "Saturation", 
    title = "Linear Regression Plot"
  )

@@

# plot graph to show relationship in Japan

brand_origin |>
  filter(group == 'Japan') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.2) +
  facet_wrap(vars(brand)) +
  scale_x_continuous(breaks=seq(50, 100, 5)) +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation",
    title = "Fig. 4: Relationship between Lightness and Saturation in Shades in Japan",
    caption = "Data source: The Pudding")

@@

In Japan, a negative linear relationship between the saturation and lightness of foundation shades is observed, as depicted in Figure 4. The data indicates that as the lightness of foundation shades increases, their saturation decreases, suggesting that lighter foundations tend to appear ashier or cooler-toned than their darker counterparts. According to a study conducted by L’Oréal, East Asian women have a skin tone range of 55-75 in lightness with warmer tones [@loreal]. The brands closest to the regression line seen in Figure 3 with the widest range in lightness and saturation are Addiction, NARS, and Shu Uemera, as demonstrated in Figure 4.

@@

The data suggest that foundation offerings in Japan tend to skew toward the fairer end of the skin tone range or significantly lighter. While there are options available for Japanese consumers to find foundation within their skin-tone range, the average foundation shade is lighter and ashier, reflecting a preference for fairer skin, and reinforcing the notion that lighter skin is more desirable. This reinforces the societal pressure to conform to certain beauty standards and can exacerbate colorism by perpetuating the notion that lighter skin is superior to darker skin tones [@japan]. The negative correlation between saturation and lightness observed in the data also implies that consumers with warmer undertones may encounter difficulties in finding foundation shades that strike the appropriate balance between warmth and lightness. Specifically, they may find that foundation shades with warm undertones are excessively dark, while those with cooler undertones are excessively light. This highlights the necessity for makeup brands to provide a diverse range of foundation shades that cater to a variety of undertones and levels of saturation.

@@

# plot graph to show relationship in India

brand_origin |>
  filter(group == 'India') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.5) +
  facet_wrap(vars(brand), scales = "free") +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation", 
    title = "Fig. 5: Relationship between Lightness and Saturation in Shades in India",
    caption = "Data source: The Pudding")

@@

Figure 5 presents a noteworthy disparity in the distribution of foundation shades across various brands concerning their lightness and saturation attributes. Specifically, it appears that domestic brands in India offer fewer foundation shades compared to international brands like L’Oréal and Maybelline. However, despite Indian skin tones falling within a lightness range of 30-65 and exhibiting warm-toned features, the majority of foundation shades offered by international brands are noticeably situated in the 70-85 lightness range [@loreal]. This observation suggests that international brands tend to prioritize whiteness more than local brands.

@@

# Appendix

## Model Testing
```{r}
#| messages: false
#| echo: false
#| warning: false
#linearity assumption
plot(model$fitted.values, model$residuals)

#normality assumption
qqnorm(model$residuals)
qqline(model$residuals)

#homoscedasticity
plot(model$fitted.values, sqrt(abs(model$residuals)), pch=20, main="Scale-Location Plot")
abline(h = mean(sqrt(abs(model$residuals))), col="red")
```

@@

# References
